Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-05 tex/main.tex
more

first-order model finders: SEM, MACE/Mace, Paradox, FMDarwin, iProver
  either direct search or reduction to SAT

@@

Nitpick
  * inductive / coinductive predicates
  * quotient types

@@

in smt : z3, cvc4 (briefly, text in main section gives detail)

@@

  * future work
    * (co)inductive predicates?
    * quotient types??

>>>>

\begin{verbatim}
first-order model finders: SEM, MACE/Mace, Paradox, FMDarwin, iProver
  either direct search or reduction to SAT

@@

Nitpick
  * nice: three-valued logic (e.g. local overflow)
    * solving a different problem:
      * no built-in notion, what's approximated is an idealized notion, no
        injections $\concret$
  * not so nice:
    one abstract domain per type, not per function argument
  * guards + one-domain per arg are a good combi, guards + one-single-domain is bad because of
    odd schemes, give unsat example

  * other features:
    * inductive / coinductive predicates
    * quotient types

@@

in smt : z3, cvc4 (briefly, text in main section gives detail)
\end{verbatim}

@@

\begin{verbatim}
  * future work
    * more eval
      * against other non-SMT-solvers (notably Leon and Nitpick)
      * problems exercising codatatypes (which CVC4 supports \cite{xxx}) and
        corecursive functions
    * more features
      * e.g. encode (co)inductive predicates as (co)recursive functions
\end{verbatim}
